Online Multiclass Linear Classification with Bandit Feedback

### 2019-01-13 ICML-submission/algorithm-for-strongly-linearly-separable-data.tex
minor

\chicheng{I think this part need to be formalized. Can we assume without loss of generality
that a deterministic prediction algorithm will have a smaller expected cost?
If so, define $F(k)$ be the number of mistake that will be made by the algorithm,
if the adversary commits to a label uniformly at random from $\cbr{1,2,\ldots,k}$,
and the guessing of the label lasts for $k$ rounds.
we can construct a recurrence of $F$: $F(k) = F(k-1) + \frac{k-1}{k}$, and $F(1) = 0$.
Therefore, $F(K) = \Omega(K)$.}

>>>>

\chicheng{I think this part need to be formalized, by directly using
~\cite{Daniely-Helbertal-2013}, Claim 2.}
%Can we assume without loss of generality
%that a deterministic prediction algorithm will have a smaller expected cost?
%If so, define $F(k)$ be the number of mistake that will be made by the algorithm,
%if the adversary commits to a label uniformly at random from $\cbr{1,2,\ldots,k}$,
%and the guessing of the label lasts for $k$ rounds.
%we can construct a recurrence of $F$: $F(k) = F(k-1) + \frac{k-1}{k}$, and $F(1) = 0$.
%Therefore, $F(K) = \Omega(K)$.
